\documentclass[]{twentysecondscv}
\usepackage{amssymb}
\usepackage{enumitem}
\usepackage{fontawesome}
\usepackage{ragged2e}



\begin{document}
	
	
%%%%%%%%%%%%%%%%%
%%PROFILE SIDE BAR%%
%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%
%%PERSONAL INFO%%%
%%%%%%%%%%%%%%%%
%\profilepic{alice.jpeg} %path of profile pic
\cvname{Davide Spataro} %your name
\cvjobtitle{Software Engineer}%your actual job position
\cvdate{}%date of birth
\cvaddress{}%address
\cvnumberphone{+39 3926580015}%telphone number
\cvmail{davide90.spataro@gmail.com}%e-mail
\cvsite{http://www.davidespataro.it}%personal site


\aboutme{ \emergencystretch 3em I am a curious and passionate software engineer and my interests include, but are not limited to, C++, parallel programming and GPGPU. I am an active \href{https://stackoverflow.com/users/1417063/davide-spataro}{StackOverflow \faStackOverflow} user, avid reader of technical and scientific books and articles, I also enjoy participating in competitive programming competitions or writing blog articles. I feel naturally inclined to working in a team, but I am also capable of  tackling and solving complex problems autonomously. 
I like to be surrounded by people I can learn from. I am passionate about classical music, photography and investing. When I am not coding I am most likely either paddling in the Mediterranean sea, lifting weights in the gym or fighting gravity on a race bike. I drink a lot of coffee \faCoffee.}%About me section

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%Skill bar section, each skill must have a value between 0 an 6 (float)%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\skills{{C and Modern C++-11-14/5},{Linux-Bash/5},{CUDA-OpenCL-MPI/4.5},{git/4.0},{CMake/3.5},{Matlab/3}, {Java/2.5}, {SQL/2.5}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%Skill text section, each skill must have a value between 0 an 6%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\skillstext{{Italian/10},{English/8.5},{Dutch/5}}

\makeprofile
%%%%%%%%%%%%%%%%%%%%
%%END PROFILE SIDE BAR%%
%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%
%%%%%%%%BODY%%%%%%%%
%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%
%%SIMPLE SECTION%%%%%%
%%%%%%%%%%%%%%%%%%%%
%\section{interests}
%The heroine and the dreamer of Wonderland;  Alice is the principal character.

\section{key skills}
\begin{twentyshort}
  \twentyitemshort
	{\small \textbf{Fundamentals}}
	{\small Algorithm and Data structure, TDD, OOP, Design Patterns}
  \twentyitemshort
    {\small \textbf{\texttt{C/C++-11+}}}
    {\small Meta-programming, standard,  boost, google test/mock libraries}
   \twentyitemshort
    {\small \textbf{Build and Version Control}}
    {\small  \texttt{git}, \texttt{GNU make}, \texttt{CMake}}
  \twentyitemshort
    {\small \textbf{Concurrency}}
    {\small  Threading, CUDA, OpenCL, MPI, OpenMP, OpenACC}
  \twentyitemshort
	{\small \textbf{OS and Scripting}}
	{\small  Linux, Bash, Windows, Python (prior experience)}
\end{twentyshort}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%TWENTY LIST ITEMS%%%%%%%%%%%%%%
%%    Four arguments: date; title; where; description %%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\section{experience}

\begin{twenty}
  \twentyitem
    {since 2018}
    {Software Design Engineer}
    {ASML, The Netherlands}
	{
		\vspace{-10pt}
		\begin{itemize}[leftmargin=*]
			\footnotesize
			\item[-] Implemented C/C++-11 core software for overlay optimization.
			\item[-] Benchmarking of metrology code aimed at improving speed of execution.
			\item[-] Adotped TDD and piloting CI transition (Jenkins).
			\item[-] Increased UT coverage for legacy C/C++ code.
		\end{itemize} 
	}
  \twentyitem
    {2017}
    {Ph.D. {\normalfont Research Visiting Student}}
    {University of Warwick, United Kingdom}
	{
		\vspace{-10pt}
		\begin{itemize}[leftmargin=*]
			\footnotesize
			\item[-] Implementation of an efficient solve for tridiagonal linear system within \href{https://github.com/OP-DSL/OPS}{OPS \faGithub}
			\item[-] Optimization using Intel SIMD intrinsics (SSE)
		\end{itemize} 
	}
  \twentyitem
    {2016}
    {Ph.D. {\normalfont Research Visiting Student}}
    {University of Edinburgh, Scotland}
	{
		\vspace{-10pt}
		\begin{itemize}[leftmargin=*]
			\footnotesize
			\item[-] Investigated parallel visualization strategies exascale simulation as part of the VELaSSCo project.
			\item[-] Prototype implementation for multi-GPU rendering using C++14.
		\end{itemize} 
	}
  \twentyitem
    {2014-2017}
    {Ph.D. {\normalfont Teaching Assistant}}
    {University of Calabria, Italy}
	{
		\vspace{-10pt}
		\begin{itemize}[leftmargin=*]
			\footnotesize
			\item[-] Teaching assistant for the course of \emph{UI and event programming} for $\approx 100$ attendees.
			\item[-] The students were, eventually, able to program a full fledged 3D videogame in Java. 
		\end{itemize} 
	}
  \twentyitem
    {2013-2014}
    {Academic Tutor}
    {University of Calabria, Italy}
    {
	    \vspace{-10pt}
	    \begin{itemize}[leftmargin=*]
	    	\footnotesize
	    	\item[-] Tutoring students for the course of \textit{object oriented programming} and \textit{algorithm and data structures}
	    \end{itemize} 
    }
\end{twenty}

\section{education}

\begin{twenty}
	\fivetwentyitem
	{2014-2018}
	{Ph.D. {\normalfont in Mathematics and Computer Science}}
	{University of Calabria, Italy}
	{\emph{Seamless acceleration of numerical regular grid methods on many-core systems.}}
	{
		\vspace{-15pt}
		\begin{itemize}[leftmargin=*]
			\footnotesize
			\item[-] Designed a DSL aimed at both efficient and quick implementation of CA and FDM on multi-core/nodes/accelearators systems \href{https://dl.acm.org/citation.cfm?id=3059134}{\faBook}.
			\item[-] Implemented a family of \texttt{C/C++/OpenCL/MPI} libraries \href{www.blablabla.it}{\faGithub} 
		\end{itemize} 
	}
	\fivetwentyitem
	{2011-2014}
	{M.Sc. magna cum laude in Computer Science}
	{University of Calabria, Italy}
	{\emph{Accelerating the new} \texttt{SCIARA-fv3} \emph{numerical model by different GPGPU strategies.}}
	{
		\vspace{-15pt}
		\begin{itemize}[leftmargin=*]
			\footnotesize
			\item[-] Investigated GPGPU parallelization for a computationally heavy fluid-dynamic model.
			\item[-] Achieved speedups up to $200x$ enabling it for risk map generation.
			\item[-] Implemented a 3D \texttt{OpenGL} interactive UI
		\end{itemize} 
	}
	\fivetwentyitem
	{2008-2011}
	{B.Sc. in Computer Science}
	{University of Calabria, Italy}
	{\texttt{B-finder}\emph{ a system for automatic detection of buildings from aerophotogrammetries.}}
	{
		\vspace{-15pt}
		\begin{itemize}[leftmargin=*]
			\footnotesize
			\item[-] Designed an active contour model like algorithm for accurate buildings segmentation from aerial images.
			\item[-] Matlab prototype implementation.
		\end{itemize} 
	}
\end{twenty}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%TWENTY LIST ITEMS%%%%%%%%%%%%%%
%%    Four arguments: date; title; where; description %%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{publications$^*$}
\footnotesize
\begin{twenty}
    \twentyitem
    {2018}
    {A first multi-GPU/multi-node implementation of the open computing abstraction layer}
    {}
    {\footnotesize{Journal of Computational Science, \url{https://doi.org/10.1016/j.jocs.2018.09.012}}}

    \twentyitem
    {2018}
    {The Open Computing Abstraction Layer for Parallel Complex Systems Modeling on Many-Core Systems}
    {}
    {\footnotesize{Journal of Parallel and Distributed Computing, Volume 121, 53-70, \url{https://doi.org/10.1016/j.jpdc.2018.07.005}}} 
    
    \twentyitem
    {2016}
    {Multi-Agent System with Multiple Group Modelling for Bird Flocking on GPU}
    {}
    {\footnotesize{Proceedings of The 2016 International Conference on Parallel, distributed and Network-Based Processing (PDP), February 17-19 2016, Crete, Greece}}
    
    
    \twentyitem
    {2015}
    {Efficient Lava Flows Simulations with OpenCL: A preliminary application for Civil Defence Purposes}
    {}
    {\footnotesize{Proceedings of The $10^{th}$ International Conference on P2P, Parallel, Grid, Cloud and Internet Computing, November 4-6, 2015, Krakow, Poland}}
%     
%    \twentyitem 
%    {2015}
%    {CUDA Dynamic Active Thread List Strategy to Accelerate Debris Flow Simulations}
%    {}
%    {\footnotesize{Proceedings of The 2015 International Conference on Parallel, Distributed and Network-Based Processing (PDP), Turku, Finland, pp 330-338}}

\end{twenty}
$^*$Full list on \url{www.davidespataro.it}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%TWENTY LIST SHORTITEMS%%%%%%%%%%%%%%
%%% Two arguments: date; title/description %%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%\begin{twentyshort}
%  \twentyitemshort
%    {1865}
%    {Chapter Five,  Advice from a Caterpillar.}
%\end{twentyshort}

%\section{Short Bio}
%He was born the $14^{th}$ February 1990 and grew up in Nicotera, a small city in Southern Italy. He attended the secondary school focusing on humanities and in 2008 he moved to Cosenza, where he studied first and then collaborated with researchers of the Department of Computer Science on the simulation of complex natural systems. His research interests revolve around the topics of `Parallel Computing' and  HPC. Since 2018 he lives in Eindhoven, working as Software Engineer at ASML for photo-lithography systems. He studied piano and music since he was eight for ten years, long enough to make him addicted to classical and jazz music. 

%%%%%%%%%%%%%%%%%%%%
%%%%%ENDBODY%%%%%%%%
%%%%%%%%%%%%%%%%%%%%

\end{document} 